### 2019-02-12 paper/birth_spacing_lit.tex
Add notes

>>>>

NFHS-2 1998-99

We use data for Uttar Pradesh (UP), the largest Indian state, which, in
the year 2000, contained 17.1\% of the country’s population
(approximately 165 million people). It has social and demographic
indicators that put it well below the Indian average (Dreze and Sen,
1997).

Birth intervals explain only a limited share of the correlation between
neonatal mortality of successive children in a family.

The main contribution of this paper is to use panel data based on
retrospective fertility histories to estimate causal effects of birth
interval length on subsequent neonatal mortality risk and of neonatal
mortality on subsequent birth interval length, controlling for
unobserved heterogeneity in both processes (referred to as frailty and
fecundity, respectively)
